The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
rm `r citep...`, for auto gen @Author_Year

## Introduction
Our inference regarding the ecological processes underlying ecological patterns
are directly linked to the scale at which they are observed `r citep(c('10.2307/1941447', '10.7312/alle06918'))`. Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability `r citep(c('10.2307/1939924', '10.1111/ele.12048'))` and global climate and productivity `r citep('10.1111/j.1365-2699.2008.01963.x')`.
Multiscale ecology has been integrated into species distribution modelling
`r citep('10.1146/annurev.ecolsys.110308.120159')`, habitat selection `r citep('10.1890/06-1672.1')`, and food webs
`r citep('10.1126/science.2740915')`. Meanwhile, in the context of animal behaviour, certain
behaviours are scale dependent, for example, acoustic communication in birds
occurs over variable spatial scales `r citep('10.1093/beheco/arp074')`. We posit that animal
behaviour and, more specifically, the social environment that animals experience
must also be scale-dependent.

@@

We thank all members of the Wildlife Evolutionary Ecology Lab, including K.
Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for
their comments on previous versions of this manuscript as well as D. Schneider
for inspiration and helpful discussions about scale. Funding for this study was
provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery
Grant to EVW.

>>>>

## Introduction
Our inference regarding the ecological processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1993; @Allen_2015]. Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability [@Legendre_1993; @Chave2013] and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling [@Elith_2009; @Mayor_2007; @Sugihara_1989], habitat selection, and food webs. Meanwhile, in the context of animal behaviour, certain
behaviours are scale dependent, for example, acoustic communication in birds
occurs over variable spatial scales [@Luther_2009]. We posit that animal
behaviour and, more specifically, the social environment that animals experience
must also be scale-dependent.

@@

We thank all members of the Wildlife Evolutionary Ecology Lab, including K.
Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for
their comments on previous versions of this manuscript as well as D. C. Schneider
for inspiration and helpful discussions about scale. Funding for this study was
provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery
Grant to EVW.
